### 2011-09-25 doc/theses/vitasek/appendix-c-trace.tex
Thesis: in progress.

Results:
Total time spent: 7754 ms
Final quality: 0.19951219512195123 (10 AMs)
Highest quality: 0.23463414634146343 (12 AMs)
Construction phase:
  Algorithm: Random
    Time taken: 248 ms
    Time since start: 248 ms
    Pool size: 10
    Quality: 0.19975609756097568 (11 AMs)
Improvement phase:
  pass #1:
  Algorithm: RandomRemove, ratio = 0.2
    Time taken: 0 ms
    Time since start: 841 ms
    Pool size: 10
    Quality: 0.15878048780487808 (9 AMs)
  pass #2:
  Algorithm: Mutation, ratio = 0.1, limit = 1 s
    Time taken: 1512 ms
    Time since start: 2710 ms
    Pool size: 11
    Quality: 0.21975609756097558 (11 AMs)

@@

  pass #10:
  Algorithm: Remove Worst
    Time taken: 80 ms
    Time since start: 7676 ms
    Pool size: 12
    Quality: 0.19951219512195123 (10 AMs)
Termination reason: Maximum iterations exceeded.

@@

% TODO make sure G.R. was introduced before! and LINK IT! swedish style!
The second section states the input file along with its size and graph representation.\\
Alpha and beta parameters for this instance belong here too.

@@

\begin{footnotesize}
\begin{verbatim}
Algorithm: Random
  Time taken: 248 ms
  Time since start: 248 ms
  Pool size: 10
  Quality: 0.19975609756097568 (11 AMs)
\end{verbatim}
\end{footnotesize}

@@

\begin{footnotesize}
\begin{verbatim}
Algorithm: Mutation, ratio = 0.1, limit = 1 s
  Time taken: 1512 ms
  Time since start: 2710 ms
  Pool size: 11
  Quality: 0.21975609756097558 (11 AMs)
\end{verbatim}
\end{footnotesize}

@@

Note that in this example trace there were no IDREF AMs found.

>>>>

Results:
Total time spent: 7754 ms
Final quality: 0.19951219512195123 (10 AMs)
Highest quality: 0.23463414634146343 (12 AMs)
Construction phase:
  Algorithm: Random
    Time taken: 248 ms / Time since start: 248 ms
    Pool size: 10
    Quality: 0.19975609756097568 (11 AMs)
Improvement phase:
  pass #1:
  Algorithm: RandomRemove, ratio = 0.2
    Time taken: 0 ms / Time since start: 841 ms
    Pool size: 10
    Quality: 0.15878048780487808 (9 AMs)
  pass #2:
  Algorithm: Mutation, ratio = 0.1, limit = 1 s
    Time taken: 1512 ms / Time since start: 2710 ms
    Pool size: 11
    Quality: 0.21975609756097558 (11 AMs)

@@

  pass #10:
  Algorithm: Remove Worst
    Time taken: 80 ms / Time since start: 7676 ms
    Pool size: 12
    Quality: 0.19951219512195123 (10 AMs)
Termination reason: Maximum iterations exceeded.

@@

The second section states the input file along with its size and graph representation (Section \ref{section-experiments-data}). Alpha and beta parameters for this instance belong here too.

@@

\begin{footnotesize}
\begin{verbatim}
Algorithm: Random
  Time taken: 248 ms / Time since start: 248 ms
  Pool size: 10
  Quality: 0.19975609756097568 (11 AMs)
\end{verbatim}
\end{footnotesize}

@@

\begin{footnotesize}
\begin{verbatim}
Algorithm: Mutation, ratio = 0.1, limit = 1 s
  Time taken: 1512 ms / Time since start: 2710 ms
  Pool size: 11
  Quality: 0.21975609756097558 (11 AMs)
\end{verbatim}
\end{footnotesize}

@@

Note that in this example trace there were no IDREF AMs found. \qed

### 2011-09-25 doc/theses/vitasek/chapter-1-definitions.tex
Thesis: in progress.

\chapter{Definitions}

@@

Now we return to \cite{fidax} to define the notion of an \textit{attribute mapping} (or AM for short). \nomenclature{AM}{Attribute Mapping}
We will use a different definition (without introducing keys from \cite{keX} for now) that will however give us the same result.

@@

\section{Independent Set}

>>>>

\chapter{Definitions}
\label{chapter-definitions}

@@

Now we return to \cite{fidax} to define the notion of an \textit{attribute mapping} (or AM for short). \nomenclature{AM}{Attribute Mapping}
We will use a different definition (without introducing keys from \cite{keX}) that will however give us the same result.

@@

\section{Independent Set}
\label{section-definitions-is}

### 2011-09-25 doc/theses/vitasek/chapter-2-research.tex
Thesis: in progress.

According to the article \cite[Chapter~4]{fidax}, the problem of finding an ID set (Section \ref{section-definitions-id-set}) with the maximal weight (Section \ref{section-definitions-weight}) is NP-hard. The article suggests a heuristic approach described in Section \ref{section-mip-fidax}, which was incorporated into the framework proposed by this work.

To the best of our knowledge, there are no other articles dealing with this problem.

TODO talk about Fajt \cite{fajt} - but that's different, that's keys. Sometimes, it is translatable, but not always.

TODO other approaches to max IS

TODO LP is simple using Simplex method, however gets hard as soon as we require some of the variables to be integral or boolean.

>>>>

According to the article \cite[Chapter~4]{fidax}, the problem of finding an ID set (Section \ref{section-definitions-id-set}) with the maximal weight (Section \ref{section-definitions-weight}) can be transformed into the maximum weighted independent set (Section \ref{section-definitions-is}) and is thus NP-hard.

TODO describe the transformation ID -> IS (other way around is in fidax)

The article suggests a heuristic approach described in Section \ref{section-mip-fidax}, which was incorporated into the framework proposed by this work.

To the best of our knowledge, there are no other articles dealing with this problem.\\

TODO talk about Fajt \cite{fajt} - but that's different, that's keys. Sometimes, it is translatable, but not always.\\

TODO our problem now is to solve max IS.

TODO other approaches to max IS - approximation methods?

### 2011-09-25 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress.

\section{Experimental Data}

@@

Consider the following XML file fragment.
\begin{verbatim}
<x>
  <y a="1" b="2"/>
  <y a="3" c="4"/>
  <y/>
  <z a="1"/>
</x>
\end{verbatim}

@@

The ``user-specified limits" of whiskers are set to default value, let us quote again from the manual.

>>>>

\section{Experimental Data}
\label{section-experiments-data}

@@

Recall the following XML file fragment from Chapter \ref{chapter-definitions}.
\begin{verbatim}
<x>
  <y a="1" b="2"/>
  <y a="3" c="4"/>
  <y/>
  <z a="1"/>
</x>
\end{verbatim}

@@

The ``user-specified limits" of whiskers are set to default value, let us quote from the manual again.
